---
title: "Burky @ EuroBillTracker"
# subtitle: "https://www.eurobilltracker.com/?referer=32954"
author: "Burky"
output:
  word_document:
    reference_docx: ebt_doc.docx
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

invisible(lapply(
  c("tidyverse", "lubridate", "flextable", "gghighlight"), # packages to load
  library, character.only = TRUE))

old <- set_flextable_defaults(font.family = "Calibri",
                              table.layout = "autofit",
                              theme_fun = theme_booktabs,
                              decimal.mark = ".",
                              big.mark = ",")

colors <- viridis::viridis(7, begin = .05, end = .95)

source("ebt_mds.txt")
ebt_mds_full <-
  ebt_mds$Date |>                    # aus den Eingabezeitpunkten ...
  full_seq(1) |>                     # einen Vektor aller moeglichen Zeitpunkte erzeugen ...
  (\(x) tibble(Date = x))() |>      # in einen Tibble umwandeln ...
  left_join(ebt_mds, by = "Date") |> # und die Daten zu den Eingabezeitpunkten einfuegen.
  mutate(Day = wday(x = Date, week_start = 1, label = TRUE, locale = "English"),
         Deno = map(.x = Deno, .f = function(x = .) c(x, double(7 - length(x))) |> as.integer()),
         Count = map_int(.x = Deno, .f = ~ sum(.)),
         Value = map_dbl(.x = Deno, .f = ~ (t(.) %*% c(5L, 10L, 20L, 50L, 100L, 200L, 500L)) |> as.integer()),
         nLoc = map_int(.x = Loc, .f = ~ length(.))
         ) |>
  select(Date, Day, Deno, Count, Value, Hits, Loc, nLoc)
```

# About

*EuroBillTracker* (EBT) is an international non-profit volunteer team dedicated to tracking Euro notes around the world. Each user enters the serial numbers and location information for each note they obtain into EuroBillTracker. From this information, the site extracts:

-   Diffusion information: Each Euro country has its own range of note serial numbers and from this information we can generate diffusion graphs that tell us how the notes travel to other countries. See the Diffusion section for more information.
-   Tracking information: When a note is re-entered, the users who previously entered it are notified via email. These hits can be seen in the statistics section.
-   Statistics and rankings: Who enters the most notes, which are the best countries? Where are the notes currently situated?

# User: Burky

## General

```{r general, include=FALSE}

days <- tibble(ebt_mds_full |> count(name = "total"),
               ebt_mds_full |> filter(Count > 0) |> count(name = "bills"),
               ebt_mds_full |> filter(Hits > 0) |> count(name = "hits"))

stat <- ebt_mds_full |> summarise(across(.cols = Count:Hits, .fns = ~ sum(., na.rm = TRUE)), .groups = "drop") |>
  bind_cols(
    ebt_mds_full |> summarise(across(.cols = Loc, .fns = ~ unlist(.) |> n_distinct()), .groups = "drop"))
```

Active contribution to EBT was recorded on **`r format(days$total, big.mark = ",")` days** between `r min(ebt_mds_full$Date)` and `r max(ebt_mds_full$Date)`. Bills were entered on `r format(days$bills, big.mark = ",")` days (= `r sprintf(days$bills / days$total * 100, fmt = '%#.2f')` %) and hits occurred on `r format(days$hits, big.mark = ",")` days (= `r sprintf(days$hits / days$total * 100, fmt = '%#.2f')` %).\
**`r format(stat$Count, big.mark = ",")` bills** (`r sprintf(stat$Count / days$total, fmt = '%#.2f')` /day) were entered with a total value of **`r format(stat$Value, big.mark = ",")` Euro** (mean = `r sprintf(stat$Value / stat$Count, fmt = '%#.2f')`); **`r format(stat$Hits, big.mark = ",")` hits** (= `r sprintf(stat$Hits / days$total, fmt = '%#.2f')` /day) occurred (hit-ratio = 1 : `r sprintf(stat$Count / stat$Hits, fmt = '%#.2f')`).\
Bills were entered in **`r format(stat$Loc, big.mark = ",")`** different **locations**.

\pagebreak

## Active Periods

*Active periods* are consecutive days with at least one bill entered. The three longest such periods were:

```{r periods, echo=FALSE}

ebt_mds_full |>
  (\(x) add_column(x, Type = rle(pull(x, Count) > 0)[[1]] |>
                     (\(y) rep(1:length(y), y))()))() |>
  group_by(Type) |> 
  summarise(Begin = min(Date),
            End = max(Date),
            Days = n(),
            Bills = sum(Count),
            Value = sum(Value),
            Hits = sum(Hits),
            BpD = (Bills / Days) |> round(1),
            Avg = (Value / Bills) |> round(2),
            HitRt = (Bills / Hits) |> round(2),
            .groups = "drop") |> 
  mutate(Type = case_when(Bills == 0 ~ "inactive",
                          TRUE ~ "active")) |> 
  arrange(desc(Days)) |>
  filter(Type == "active") |> 
  select(-Type) |> 
  head(3) -> tmp
# knitr::kable(tmp, format.args = list(big.mark = ','))
flextable(data = tmp) |>
  vline(j = "End", part = "all") |> 
  align(align = "left", part = "header", j = 1:2) |> 
  footnote(value = as_paragraph(c(" Bills/Day", " Value/Bill", " Bills/Hit")),
           ref_symbols = letters[1:3], inline  = TRUE, part = "header", j = 7:9) |> 
  fontsize(size = 9, part = "footer")
```

 \

The **three longest periods** cover **`r format(sum(tmp$Days), big.mark = ",")` days** (= `r sprintf(sum(tmp$Days) / days$total * 100, fmt = '%#.2f')`%), **`r format(sum(tmp$Bills), big.mark = ",")` bills** (= `r sprintf(sum(tmp$Bills) / stat$Count * 100, fmt = '%#.2f')`%), a total value of **`r format(sum(tmp$Value), big.mark = ",")` Euro** (= `r sprintf(sum(tmp$Value) / stat$Value * 100, fmt = '%#.2f')`%) and **`r format(sum(tmp$Hits), big.mark = ",")` hits** (= `r sprintf(sum(tmp$Hits) / stat$Hits * 100, fmt = '%#.2f')`%).

## Yearly Activity

Active contribution to EBT was recorded in `r (substr(ebt_mds_full$Date, 1, 4) |> unique() |> length())` different years. Cumulative entries throughout the recent years look like:

```{r year1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=9/16}

last <- 3

ebt_mds_full |> 
  select(Date, Count) |> 
  mutate(Days = 1,
         Year = year(Date),
         Time = yday(Date)) |> 
  group_by(Year) |> 
  mutate(cumDays = cumsum(Days),
         cumCount = cumsum(Count),
         cumEntRt = cumCount / cumDays) |>
  ungroup() |>
  ggplot() +
  aes(x = Time, y = cumEntRt) +
  geom_line(mapping = aes(color = factor(Year), group = Year), linewidth = 1.5,  alpha = .67) +
  gghighlight(max(Year), max_highlight = last, label_key = Year,
              unhighlighted_params = list(linewidth = .5, color = "grey")) +
  scale_x_continuous(name = paste0("Time Elapsed (Days)"), breaks = function(x) seq(0, x[2], by = 60), expand = expansion(mult = c(0, .01))) +
  scale_y_continuous(name = "Cumulative Entry Rate", expand = expansion(mult = .02)) +
  scale_color_manual(name = "", values = c(colors[c(7, 4, 1)], "grey85")) +
  theme_minimal() -> p

plot(p)

rm(last, p)
```

\pagebreak

## Monthly Activity

Active contribution to EBT was recorded in `r (substr(ebt_mds_full$Date, 1, 7) |> unique() |> length())` different months. The seven month with **most** entered bills were:

```{r months, echo=FALSE}

ebt_mds_full |>
  # Zusammenfassen der Daten pro Monat
  group_by(Month = floor_date(Date, unit = "month") |> str_sub(1, 7)) |> 
  summarise(Days = n(),
            Bills = sum(Count, na.rm = TRUE),
            Value = sum(Value, na.rm = TRUE),
            Hits = sum(Hits, na.rm = TRUE),
            BpD = (Bills / Days) |> round(1),
            Avg = (Value / Bills) |> round(2),
            HitRt = (Bills / Hits) |> round(2),
            .groups = "drop") |> 
  arrange(desc(Bills)) -> tmp
# knitr::kable(head(tmp, 5), format.args = list(big.mark = ','))
flextable(data = head(tmp, 7)) |>
  vline(j = "Month", part = "all") |> 
  footnote(value = as_paragraph(c(" Bills/Day", " Value/Bill", " Bills/Hit")),
           ref_symbols = letters[1:3], inline  = TRUE, part = "header", j = 6:8) |> 
  fontsize(size = 9, part = "footer")
```

 \

The seven months with **least** entered bills were:

```{r months2, echo=FALSE}

# knitr::kable(tail(tmp, 5), format.args = list(big.mark = ','))
flextable(data = tail(tmp, 7)) |>
  vline(j = "Month", part = "all") |> 
  footnote(value = as_paragraph(c(" Bills/Day", " Value/Bill", " Bills/Hit")),
           ref_symbols = letters[1:3], inline  = TRUE, part = "header", j = 6:8) |> 
  fontsize(size = 9, part = "footer")
```

 \

\pagebreak

Graphical representation of the monthly variation:

```{r month3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=9/16}

ebt_grpd <- ebt_mds_full |>
  # Zusammenfassen der Daten pro Monat
  group_by(Month = ceiling_date(Date, unit = "month") - days(1)) |> 
  summarise(Days = n(),
            Count = sum(Count, na.rm = TRUE),
            Value = sum(Value, na.rm = TRUE),
            Hits = sum(Hits, na.rm = TRUE),
            Loc = Loc |> unlist() |> unique() |> length(),
            .groups = "drop")

# Korrigieren der Daten mit den Tagen, abgeleitete Variablen und Farben aktuelle Periode
p_dat <- ebt_grpd  |>
  mutate(AvgValue = Value / Count,
         HitRt = Count / Hits,
         Color = c(rep("old", n() - 1), "recent")) |> 
  mutate_at(vars(Count, Value, Hits), .f = ~ (. / Days)) |> 
  # Ueberfuehren der Spalten in eine Variable
  gather(-Month, -Days, -Color, key = "What", value = "Count") |>
  # Festlegen der Reihenfolge der Plots
  mutate(What = What |>
           factor(levels = c("Count", "Value", "AvgValue", "Hits", "HitRt", "Loc"),
                  labels = c("Bills per Day", "Value per Day", "Avg Value", "Hits per Day", "Hit-Ratio (1 : ..)", "Locations")))
# Definieren des Plots
p <- ggplot(data = p_dat, mapping = aes(x = Month, y = Count)) + 
  geom_point(mapping = aes(color = Color), shape = 4, size = 0.8, alpha = 0.65, show.legend = FALSE) +
  geom_smooth(color = colors[2], method = "loess", span = 1.5 / log(ebt_grpd$Month |> length()),  se = FALSE) +
  scale_x_date(name = "Time", date_breaks = "4 years", date_labels = "%Y", expand = c(.01, .01)) +
  scale_y_continuous(name = "", expand = c(.02, .02)) +
  scale_color_manual(values = c("old" = colors[5], "recent" = colors[6])) +
  facet_wrap(~ What, scales = "free_y", ncol = 2) +
  theme_minimal()

# Plot
plot(p)
```

\pagebreak

## Denomination

Distribution of entered bills by denomination:

```{r denomination, echo=FALSE}

ebt_deno <- ebt_mds_full |> 
  select(Date, Deno) |> 
  transmute(Date, map_dfr(Deno, ~ set_names(., paste0("E", sprintf("%03d", c(5, 10, 20, 50, 100, 200, 500))))))

ebt_deno |> select(-Date) |> 
  pivot_longer(cols = `E005`:`E500`, names_to = "Denom", values_to = "Count") |> 
  group_by(Denom) |> 
  summarise(Count = sum(Count), .groups = "drop") |> 
  mutate(Val = substr(Denom, 2, 4) |> as.integer(),
         Denom = factor(Denom, labels = paste0("\u20ac ", # EURO symbol
                                               str_pad(c(5, 10, 20, 50, 100, 200, 500), width = 3, side = "left"))),
         Value = Count * Val,
         C_Pct = (Count / sum(Count) * 100) |> round(2),
         V_Pct = (Value / sum(Value) * 100) |> round(2)) |> 
  select(Denom, Count, C_Pct, Value, V_Pct) -> tmp
# knitr::kable(tmp, format.args = list(big.mark = ','))
flextable(tmp) |>
  vline(j = "Denom", part = "all") |> 
  footnote(value = as_paragraph(c(" % of total Count", " % of total Value")),
           ref_symbols = letters[1:2], inline  = TRUE, part = "header", j = c(3, 5)) |> 
  fontsize(size = 9, part = "footer")
```

 \

Distribution of denominations by year:

```{r yearly, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=9/16}

ebt_deno |> 
  group_by(Year = lubridate::year(Date)) |> 
  summarise(across(.cols = `E005`:`E500`, .fns = sum), .groups = "drop") |> 
  pivot_longer(cols = `E005`:`E500`, names_to = "Denom", values_to = "Count") |> 
  mutate(Denom = factor(Denom, labels = paste0("\u20ac ", c(5, 10, 20, 50, 100, 200, 500)))) -> tmp # EURO symbol

p <- ggplot(data = tmp, mapping = aes(x = Year, y = Count, group = Denom)) +
  geom_bar(mapping = aes(fill = Denom), stat = "identity") +
  scale_x_continuous(expand = c(.01, .01)) +
  scale_y_continuous(name = "Count [k]", labels = function(x) x / 1000, expand = c(.02, .02)) +
  scale_fill_viridis_d(direction = -1, begin = .05, end = .95) +
  theme_minimal()

plot(p)
```

\pagebreak

## Hits

The five longest hit streaks were:

```{r hits, echo=FALSE, message=FALSE}

nth_max <- function(x, n) unique(sort(x, decreasing = TRUE))[n]

ebt_mds_full |>
  (\(x) add_column(x, Type = rle(pull(x, Hits) > 0)[[1]] |>
                     (\(y) rep(1:length(y), y))()))() |>
  group_by(Type) |> 
  summarise(Begin = min(Date),
            End = max(Date),
            Days = n(),
            Bills = sum(Count),
            Value = sum(Value),
            Hits = sum(Hits),
            BpD = (Bills / Days) |> round(1),
            Avg = (Value / Bills) |> round(2),
            HitRt = (Bills / Hits) |> round(2),
            .groups = "drop") |> 
  mutate(Type = case_when(Hits == 0 ~ "inactive",
                          TRUE ~ "active")) |> 
  filter(Type == "active") -> streaks

  streaks |> 
    arrange(desc(Days), HitRt) |> 
    filter(Days >= nth_max(Days, 5)) |> 
    select(-Type) -> tmp

  # list of symbols
  symb <- c(letters, "\u002A", "\u2020", "\u2021") # last three are asterisk, dagger, double dagger
  
  # for later plots
  dat <- streaks |> arrange(Begin) |> tail(15)
  dat0 <- semi_join(tmp, dat) |>
    mutate(Mid = as_date(Begin  + as.duration(interval(Begin, End)) / 2)) |> 
    rowid_to_column(var = "#") |> 
    mutate(`#` = symb[`#`])
  
  tmp <- left_join(tmp, dat0 |> select(`#`, Begin, End)) |>
    # replace_na(list(`#`= "&#0000;")) |> # Null symbol (HTML)
    replace_na(list(`#`= " ")) |> 
    relocate(`#`)
  
# knitr::kable(tmp, format.args = list(big.mark = ','))
flextable(tmp) |>
  vline(j = "End", part = "all") |> 
  align(align = "left", part = "header", j = 2:3) |> 
  footnote(value = as_paragraph(c(" Bills/Day", " Value/Bill", " Bills/Hit")),
           ref_symbols = letters[1:3], inline  = TRUE, part = "header", j = 7:9) |> 
  fontsize(size = 9, part = "footer")
```

 \

Plot of the 15 most recent hit streaks:

```{r hits2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=9/16}

p <- ggplot() +
  geom_rect(data = dat, mapping = aes(xmin = Begin - .5, xmax = End + .5, ymin = 0, ymax = Hits/Days, fill = HitRt)) +
  geom_rect(data = dat0, mapping = aes(xmin = Begin - .5, xmax = End + .5, ymin = 0, ymax = Hits/Days), fill = NA, color = "grey25") +
  geom_text(data = dat0, mapping = aes(x = End - days(2), y = Hits/Days + .15, label = `#`)) +
  scale_x_date(name = "Time", date_labels = "%m/%Y", expand = c(.01, .01)) +
  scale_y_continuous(name = "Hits per Day", expand = c(.02, .02)) +
  scale_fill_viridis_c(name = "Hit Ratio", direction = -1, begin = .05, end = .95) +
  theme_minimal()

plot(p)
```

\pagebreak

## Equal Bills Day

*Equal Bills Day* is the first day after the end of a calendar year that the number of bills entered in that calender year is met or exceeded. The *Equal Bills Days* so far are:

```{r ebd, echo=FALSE}

ebd <- function(year = NULL){
  
  # Libraries ----
  library(tidyverse)
  library(lubridate)
  
  # Calculate ----
  ## Get Data
  dat <- ebt_mds |>
    transmute(Date, Count = map_int(.x = Deno, .f = ~ as.integer(sum(.x))))
  
  ## Get 'count' to look for in the future
  count <- dat |> 
    filter(year(Date) == year) |> 
    pull(Count) |> 
    sum()
  
  ## Find EBD
  ebd <- dat |> 
    filter(year(Date) > year) |> 
    mutate(CumCount = cumsum(Count)) |> 
    filter(CumCount >= count) |> 
    head(1)
  ## Handle empty result
  if(tally(ebd) == 0) ebd <- NA else
    ebd <- ebd$Date
  
  ## Calculate duration to reach EBD
  dur <- as.numeric(
    difftime(ebd, date(
      paste(year, "12", "31", sep = "-")),
      units = "days"))
  
  # Result ----
  # Build result df
  res <- data.frame(
    Selection = year |> as.character(),
    Count = count,
    EBDay = ebd,
    Days = dur,
    asY = round(dur / 365, 2))
  
  # Return Result
  return(res)
  
  # Clean up ----
  rm(year, count, ebd, dur)
}

map_df(2004:format(Sys.Date(), "%Y"), ~ebd(.)) |>
  rename(Year = Selection) -> tmp

flextable(data = tmp) |>
  vline(j = "Count", part = "all") |> 
  footnote(value = as_paragraph(c(" Equal Bills Day", " Days/365")),
           ref_symbols = letters[1:2], inline  = TRUE, part = "header", j = c(3, 5)) |> 
  fontsize(size = 9, part = "footer")
```


```{r end, include=FALSE}
do.call(set_flextable_defaults, old)
```
