---
title: "EuroBillTracker"
subtitle: "https://www.eurobilltracker.com/?referer=32954"
author: "Burky"
output:
  word_document:
    reference_docx: ebt_doc.docx
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)

colors <- viridis::viridis(7, begin = .05, end = .95)

source("ebt_mds.txt")
ebt_mds_full <-
  ebt_mds$Date %>%                    # aus den Eingabezeitpunkten ...
  full_seq(1) %>%                     # einen Vektor aller m?glichen Zeitpunkte erzeugen ...
  tibble(Date = .) %>%                # in einen Tibble umwandeln ...
  left_join(ebt_mds, by = "Date") %>% # und die Daten zu den Eingabezeitpunkten einf?gen.
  mutate(Day = lubridate::wday(x = Date, week_start = 1, label = TRUE),
         Deno = purrr::map(.x = Deno, .f = function(x = .) c(x, double(7 - length(x))) %>% as.integer()),
         Count = map_int(.x = Deno, .f = ~ sum(.)),
         Value = map_dbl(.x = Deno, .f = ~ (t(.) %*% c(5L, 10L, 20L, 50L, 100L, 200L, 500L)) %>% as.integer()),
         nLoc = map_int(.x = Loc, .f = ~ length(.))) %>%
  select(Date, Day, Deno, Count, Value, Hits, Loc, nLoc)
# Immer englische Abk?rzungen f?r die Wochentage verwenden [wday() nimmt aus locale()]
levels(ebt_mds_full$Day) <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")

rm(ebt_mds)
```

# About
EuroBillTracker (EBT) is an international non-profit volunteer team dedicated to tracking Euro notes around the world. Each user enters the serial numbers and location information for each note they obtain into EuroBillTracker. From this information, the site extracts:

* Diffusion information: Each Euro country has its own range of note serial numbers and from this information we can generate diffusion graphs that tell us how the notes travel to other countries. See the Diffusion section for more information.
* Tracking information: When a note is re-entered, the users who previously entered it are notified via email. These hits can be seen in the statistics section.
* Statistics and rankings: Who enters the most notes, which are the best countries? Where are the notes currently situated?

# User Burky
## General
```{r general, include=FALSE}

days <- tibble (total = ebt_mds_full %>% nrow(),
                bills = ebt_mds_full %>% filter(Count >0 ) %>% nrow(),
                hits = ebt_mds_full %>% filter(Hits >0 ) %>% nrow())
stat <- ebt_mds_full %>% summarise(across(.cols = Count:Hits, .fns = ~ sum(., na.rm = TRUE)), .groups = "drop") %>%
  bind_cols(
    ebt_mds_full %>% summarise(across(.cols = Loc, .fns = ~ unlist(.) %>% n_distinct()), .groups = "drop")
  )
```
Activity was recorded on **`r days$total %>% format(big.mark = ",")` days** between `r min(ebt_mds_full$Date)` and `r max(ebt_mds_full$Date)`. Bills were entered on `r days$bills %>% format(big.mark = ",")` days (= `r (days$bills / days$total * 100) %>% sprintf(., fmt = '%#.2f')` %) and hits occured on `r days$hits %>% format(big.mark = ",")` days (= `r (days$hits / days$total * 100) %>% sprintf(., fmt = '%#.2f')` %).  
**`r stat$Count %>% format(big.mark = ",")` bills** (`r (stat$Count / days$total) %>% sprintf(., fmt = '%#.2f')` /day) were entered with a total value of **`r stat$Value %>% format(big.mark = ",")` Euro** (mean = `r (stat$Value / stat$Count) %>% sprintf(., fmt = '%#.2f')`).  
**`r stat$Hits %>% format(big.mark = ",")` hits** (= `r (stat$Hits / days$total) %>% sprintf(., fmt = '%#.2f')` /day) occured (hit-ratio = 1 : `r (stat$Count / stat$Hits) %>% sprintf(., fmt = '%#.2f')`).  
Bills were entered in **`r stat$Loc %>% format(big.mark = ",")`** different **locations**.

\pagebreak
## Active Periods
The five longest active periods were:
```{r periods, echo=FALSE}

ebt_mds_full %>% 
  add_column(Type = (pull(., Count) > 0) %>%
               rle() %>%
               `[[`(1) %>%
               rep(1:length(.), .)) %>%
  group_by(Type) %>% 
  summarise(From = min(Date),
            To = max(Date),
            Days = n(),
            Bills = sum(Count),
            Value = sum(Value),
            Hits = sum(Hits),
            BpD = (Bills / Days) %>% round(1),
            Avg = (Value / Bills) %>% round(2),
            HitRt = (Bills / Hits) %>% round(2),
            .groups = "drop") %>% 
  mutate(Type = case_when(Bills == 0 ~ "inactive",
                          TRUE ~ "active")) %>% 
  arrange(desc(Days)) %>%
  filter(Type == "active") %>% 
  select(-Type) %>% 
  head(5) -> tmp
  knitr::kable(tmp, format.args = list(big.mark = ','))

```

The **five longest periods** cover **`r sum(tmp$Days) %>% format(big.mark = ",")` days** (= `r (sum(tmp$Days) / days$total * 100) %>% sprintf(., fmt = '%#.2f')`%), **`r sum(tmp$Bills) %>% format(big.mark = ",")` bills** (= `r (sum(tmp$Bills) / stat$Count * 100) %>% sprintf(., fmt = '%#.2f')`%), a total value of **`r sum(tmp$Value) %>% format(big.mark = ",")` Euro** (= `r (sum(tmp$Value) / stat$Value * 100) %>% sprintf(., fmt = '%#.2f')`%) and **`r sum(tmp$Hits) %>% format(big.mark = ",")` hits** (= `r (sum(tmp$Hits) / stat$Hits * 100) %>% sprintf(., fmt = '%#.2f')`%).

## Yearly Activity
Entries throughout the year:

```{r year1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=0.5625}

top <- 3

p <- ebt_mds_full %>%
  arrange(Date) %>% 
  mutate(Year = year(Date),
         Year2 = case_when(Year < (max(Year) - top + 1) ~ "older",
                           TRUE ~ as.character(Year)),
         Course = yday(Date)) %>% 
  group_by(Year) %>% 
  mutate(cumCount = cumsum(Count)) %>% 
  ungroup() %>% 
  ggplot(data = ., mapping = aes(x = Course, y = cumCount)) +
#  geom_abline(slope = c(100, 200, 300), color = "grey67", linetype = "dashed", size = 1) +
  geom_line(mapping = aes(group = Year, color = Year2, size = Year2), alpha = .6) +
  scale_x_continuous(name = "Course (day of year)", expand = c(.01, .01)) +
  scale_y_continuous(name = "Cumulative count [k]", labels = function(x) x / 1000, expand = c(.02, .02)) +
  scale_color_manual(name = "", values = c(colors[c(7, 4, 1)], "grey85")) +
  scale_size_manual(name = "", values = c(rep(2.5, top), 1)) +
  theme_minimal()

plot(p)

rm(top, p)
```

\pagebreak
## Monthly Activity
The five most active months were:
```{r months, echo=FALSE}

ebt_mds_full %>%
  # Zusammenfassen der Daten pro Monat
  group_by(Month = floor_date(Date, unit = "month") %>% str_sub(1, 7)) %>% 
  summarise(Days = n(),
            Bills = sum(Count, na.rm = TRUE),
            Value = sum(Value, na.rm = TRUE),
            Hits = sum(Hits, na.rm = TRUE),
            BpD = (Bills / Days) %>% round(1),
            Avg = (Value / Bills) %>% round(2),
            HitRt = (Bills / Hits) %>% round(2),
            .groups = "drop") %>% 
  arrange(desc(Bills)) -> tmp
  knitr::kable(head(tmp, 5), format.args = list(big.mark = ','))

```

The five least active months were:
```{r months2, echo=FALSE}

knitr::kable(tail(tmp, 5), format.args = list(big.mark = ','))

```

Graphical representation of the monthly variation:

```{r month3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=0.5625}

ebt_grpd <- ebt_mds_full %>%
  # Zusammenfassen der Daten pro Monat
  group_by(Month = ceiling_date(Date, unit = "month") - days(1)) %>% 
  summarise(Days = n(),
            Count = sum(Count, na.rm = TRUE),
            Value = sum(Value, na.rm = TRUE),
            Hits = sum(Hits, na.rm = TRUE),
            Loc = Loc %>% unlist() %>% unique() %>% length(),
            .groups = "drop")

# Korrigieren der Daten mit den Tagen, abgeleitete Variablen und Farben aktuelle Periode
p_dat <- ebt_grpd  %>%
  mutate(AvgValue = Value / Count,
         HitRt = Count / Hits,
         Color = c(rep("old", n() - 1), "recent")) %>% 
  mutate_at(vars(Count, Value, Hits), .f = ~ (. / Days)) %>% 
  # Überführen der Spalten in eine Variable
  gather(-Month, -Days, -Color, key = "What", value = "Count") %>%
  # Festlegen der Reihenfolge der Plots
  mutate(What = What %>%
           factor(levels = c("Count", "Value", "AvgValue", "Hits", "HitRt", "Loc"),
                  labels = c("Bills per Day", "Value per Day", "Avg Value", "Hits per Day", "Hit-Ratio (1 : ..)", "Locations")))
# Definieren des Plots
p <- ggplot(data = p_dat, mapping = aes(x = Month, y = Count)) + 
  geom_point(mapping = aes(color = Color), shape = 4, size = 0.8, alpha = 0.65, show.legend = FALSE) +
  geom_smooth(color = colors[2], method = "loess", span = 1.5 / log(ebt_grpd$Month %>% length()),  se = FALSE) +
  scale_x_date(name = "Time", date_breaks = "2 years", date_labels = "%Y", expand = c(.01, .01)) +
  scale_y_continuous(name = "", expand = c(.02, .02)) +
  scale_color_manual(values = c("old" = colors[5], "recent" = colors[7])) +
  facet_wrap(~ What, scales = "free_y", ncol = 2) +
  theme_minimal()

# Plot
plot(p)
```

\pagebreak
## Denomination
Distribution of entered bills by denomination:
```{r denomination, echo=FALSE}

ebt_mds_full$Deno %>%
  do.call(rbind, .) %>%
  as_tibble(.name_repair = "minimal") %>%
  setNames(., paste0("E", c(5, 10, 20, 50, 100, 200, 500) %>% sprintf("%03d", .))) %>% 
  gather(key = Denomination, value = Count) %>% 
  group_by(Denomination) %>% 
  summarise(Count = sum(Count), .groups = "drop") %>% 
  mutate(Val = substr(Denomination, 2, 4) %>% as.integer(),
         Denomination = factor(Denomination, labels = c(5, 10, 20, 50, 100, 200, 500) %>%
                                 stringr::str_pad(., width = 3, side = "left") %>% 
                                 paste0("€  ", .)),
         Value = Count * Val,
         C_Pct = (Count / sum(Count) * 100) %>% round(., 2),
         V_Pct = (Value / sum(Value) * 100) %>% round(., 2)) %>% 
  select(Denomination, Count, C_Pct, Value, V_Pct) -> tmp
  knitr::kable(tmp, format.args = list(big.mark = ','))

```

Distribution of denominations by year:

```{r yearly, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=0.5625}

ebt_mds_full %>% 
  mutate(map_dfr(Deno, ~ set_names(., paste0("€  ", c(5, 10, 20, 50, 100, 200, 500))))) %>% 
  group_by(Year = lubridate::year(Date)) %>% 
  summarise(across(.cols = `€  5`:`€  500`, .fns = sum), .groups = "drop") %>% 
  #summarise_at(.vars = vars(`€  5`:`€  500`), .f = ~ sum(.), .groups = "drop") %>% 
  gather(-Year, key = Denomination, value = Count) %>% 
  mutate(Denomination = factor(Denomination, levels = paste0("€  ", c(5, 10, 20, 50, 100, 200, 500))))-> tmp

p <- ggplot(data = tmp, mapping = aes(x = Year, y = Count, group = Denomination)) +
  geom_bar(mapping = aes(fill = Denomination), stat = "identity") +
  scale_x_continuous(expand = c(.01, .01)) +
  scale_y_continuous(name = "Count [k]", labels = function(x) x / 1000, expand = c(.02, .02)) +
  scale_fill_viridis_d(name = "Denom.", direction = -1, begin = .05, end = .95) +
  theme_minimal()

plot(p)

```

\pagebreak
## Hits
The five longest hit streaks were:
```{r hits, echo=FALSE}

nth_max <- function(x, n) unique(sort(x, decreasing = TRUE))[n]

ebt_mds_full %>% 
  add_column(Type = (pull(., Hits) > 0) %>%
               rle() %>%
               `[[`(1) %>%
               rep(1:length(.), .)) %>%
  group_by(Type) %>% 
  summarise(From = min(Date),
            To = max(Date),
            Days = n(),
            Bills = sum(Count),
            Value = sum(Value),
            Hits = sum(Hits),
            BpD = (Bills / Days) %>% round(1),
            Avg = (Value / Bills) %>% round(2),
            HitRt = (Bills / Hits) %>% round(2),
            .groups = "drop") %>% 
  mutate(Type = case_when(Hits == 0 ~ "inactive",
                          TRUE ~ "active")) %>% 
  filter(Type == "active") -> streaks
  streaks %>% 
    arrange(desc(Days), HitRt) %>% 
    filter(Days >= nth_max(Days, 5)) %>% 
    select(-Type) -> tmp
  knitr::kable(tmp, format.args = list(big.mark = ','))

```

Plot of last 21 hit streaks:

```{r hits2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7.5, fig.asp=0.5625}

p <- streaks %>% arrange(From) %>% tail(21) %>%
  ggplot() +
  geom_rect(mapping = aes(xmin = From - .5, xmax = To + .5, ymin = 0, ymax = Hits/Days, fill = HitRt)) +
  scale_x_date(name = "Time", date_labels = "%m/%Y", expand = c(.01, .01)) +
  scale_y_continuous(name = "Hits per Day", expand = c(.02, .02)) +
  scale_fill_viridis_c(name = "Hit ratio", direction = -1, begin = .05, end = .95) +
  theme_minimal()

plot(p)

```
